%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Soleiman Anwary (soleiman.anwary@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4
% Command for printing skill overview bubbles

% \newcommand\skills{ 
% ~
% 	\smartdiagram[bubble diagram]{
%         \textbf{Coursera}\\\textbf{Courses}\\\textbf{Completed},
%         \textbf{Data}\\\textbf{Structures},
%         \textbf{~~~IBM Data~}\\\textbf{Science}\\\textbf{Course},
%         \textbf{~~~Machine~~~}\\\textbf{~~Learning~~}\\\textbf{Stanford}\\\textbf{University},
%         \textbf{Deep}\\\textbf{Learning}
%     }
% }
%----------------------------------------------------------------------------------------
%   I have written down the extra-curricular projects I have done in the section below for the PROJECTS header in the left panel. 
%----------------------------------------------------------------------------------------
\python{
\textbf{Python}
\vspace{-2mm}
\begin{itemize}
    \item Numpy, Scipy, Sklearn, \\Pandas, Matplotlib, Plotly
\end{itemize}

\textbf{SQL} 
\vspace{-2mm}
\begin{itemize}
    \item MySQL; structure, author and manage databases.
\end{itemize}

\textbf{UNIX}
\vspace{-2mm}
\begin{itemize}
    \item Experienced with Unix \& emacs.
\end{itemize}

\textbf{Tableau and \LaTeX} 
\vspace{-2mm}
\begin{itemize}
    \item Can create user dashboards and manage data streams.
\end{itemize}
\vspace{-4mm} % Reduce the space between the last point in Skills and the Projects header 
} 

\projects{
\flushleft \textbf{Consultant Engineer Pyropower}
    \vspace{-5mm}
    \justifying{ % fully justifies the text 
    \begin{itemize}
        \item Structured the strategy of design for a portable biofuel power plant. 
    \end{itemize}
    }

\flushleft \textbf{Tsinghua Summer School 2018}
    \vspace{-5mm}
    \justifying{ % fully justifies the text 
    \begin{itemize}
        \item Collaborated with international students on a project comparing Li-ion batteries and Hydrogen Fuel Cells. 
        \item We presented our final project to a panel of experts at Tsinghua University in Beijing, China. 
    \end{itemize}
    }
    \vspace{-4mm}
}

% Programming skill bars -- this is not relevant for a consultancy position. 

% \programming{{R / 1.5},{Java $\textbullet$ SQL / 2.5}, {Matlab $\textbullet$ Python $\textbullet$ \large \LaTeX / 4}}

%----------------------------------------------------------------------------------------
%   I have written down my languages and then clubs and societies that I am part of.  
%----------------------------------------------------------------------------------------
\education{
\textbf{English, German, Farsi} 
\begin{itemize}
    \item Fluent in all three languages.
\end{itemize}
}

\clubs{
\begin{itemize}
    \item \textbf{Founder} of Ethics in Soc(AI)ty, \\
    Imperial College London 
    \item Imperial College Basketball
\end{itemize}

}
%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{Soleiman N. \\ \\
Anwary} % Your name
\cvjobtitle{Process Systems Engineering finalist interested in Computational Statistics and Data Science} % Current Role ----- ...with an interest in AI and its applications in energy.
% title/career

\cvlinkedin{/in/sanwary}
\cvgithub{Sol3iman} %Sol3iman Once you have put 1 project up. 
\cvnumberphone{(+44) 7456747347} % Phone number
\cvsite{} % Personal website
\cvmail{sna314@ic.ac.uk} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Education}
\begin{twenty} % Environment for a list with descriptions
\twentyitem
    	{Oct. 2017-}
		{Present}
        {Imperial College London}
        {\href{http://www.imperial.ac.uk}{Engineering, MEng - 2.1}}
        {}
        {\vspace{-2mm} \begin{itemize}
            \item I am a Chemical and Process System Engineering finalist working on AI PID control using machine learning techniques such as policy gradient methods in Reinforcement Learning and deep neural nets.
            \item I am focussing on advanced optimisation and operations research as well as dynamic systems in my final year. 
        \end{itemize}%add itemise here 
        }
        \\

\twentyitem
    	{Oct. 2014-}
		{Jun. 2016}
        {University of Cambridge, St. Catharine's College}
        {\href{http://www.cam.ac.uk}{Medicine, MBBS}}
        {}
        {\vspace{-2mm} \begin{itemize}
            \item I studied Medicine as part of the Medical and Natural Sciences Tripos before pursuing a degree in Engineering.
        \end{itemize}
        }
        \\
\twentyitem
    	{Sept. 2011 -}
		{Jun. 2014}
        {Canons High School}
        {\href{http://www.canons.harrow.sch.uk}{GCSEs and A-levels}}
        {}
        {\vspace{-2mm} \begin{itemize}
            \item 10 A*s at GCSE and 5 A*s at A-level for Maths, Physics, Chemistry, Biology, and EPQ (99\% average).
        \end{itemize}
        }
        \\
\twentyitem
        {Jun. 2014-}
        {Present}
        {Awards \& Prizes}
        {}
        {}
        {\vspace{-2mm} \begin{itemize}
            \item I am a Thermo Fisher Engineering Scholar; Crest Gold Award for excellence in undergraduate research.
            \item Nuffield Science \nth{1} Prize for modelling of blood vessel generation.
            %\item Cambridge Chemistry Challenge Gold Award (\textit{top 10\%})
            \item SensUs Biosensor Design Finalist 2019.
        \end{itemize}
        }
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 Work Experience (Write a research section after this)
%----------------------------------------------------------------------------------------
\section{Experience}
\begin{twenty}
    \twentyitem
        {Jun. 2020-}
        {Oct. 2020}
        {BlackRock}
        {\href{http://www.blackrock.com}{Portfolio Analytics Group, Data Science}}
        {}
        {\vspace{-1mm} \begin{itemize}
            \item Created a data pipeline for ESG data vendors like Morningstar. 
            \item Designed a data dashboard for ESG risk profiles using Plotly, Tableau.
            \item Developed a deep understanding of \textbf{financial markets}.
            \item \textbf{Presented} the dashboard to portfolio managers and stakeholders. 
            \item Learned about the Aladdin software suite and Explore (BlackRock) portfolio software
        \end{itemize}
        }
    \end{twenty}
    
\begin{twenty}
    \twentyitem
        {Jun. 2019-}
        {Sept. 2019}
        {SensUs Biosensor Competition}
        {\href{http://www.sensus.org}{Engineering Lead}}
        {}
        {\vspace{-1mm} \begin{itemize}
            \item Worked as part of a team of 11 Imperial students to develop a biosensor prototype for the treatment of arthritis. 
            \item Managed 4 engineers to work under stringent time constraints.
            \item \textbf{Presented} our prototype and poster at the 2019 Eindhoven SensUs competition final to a senior panel of judges. \vspace{1mm}
        \end{itemize}
        }
    \end{twenty}
    
\begin{twenty}

	\twentyitem
    	{Mar. 2019}
		{(1 week)}
        {Deutsche Bank}
        {\href{http://www.db.com}{Technology Spring Intern}}
        {}
        {
        {\vspace{-1mm} \begin{itemize} 
        \item Learned about software testing, agile project work methodologies including waterfall and scrum which I later \textbf{implemented} in my end of year project to achieve a first class grade. 
        \item Came \nth{1} in the "Hack the Bank" coding challenge where tasks such as creating a basic algorithm for buying gold, and writing a security script to prevent brute force SQL attacks. \vspace{1mm}
        % \item \textbf{Tools used}: R, Python, scikit-learn, pandas 
		\end{itemize}}
        }
\end{twenty}

\begin{twenty}
    \twentyitem
        {Jul. 2018-}
        {Oct. 2018}
        {Signol ltd.}
        {\href{http://www.signol.io}{Data Science Intern}}
        {}
        {\vspace{-1mm} \begin{itemize}
            \item \textbf{Managed} the initial stages of the data life-cycle from the data collection to cleaning, and visualisation of aviation data from 2 airlines. 
            % \item The objective was to ascertain relationships between behavioural changes among pilot captains and fuel usage using logistic regression analysis. 
            % \item Created detailed documentation for flight variable data and process flowcharts to break down aviation fuel saving behaviours among pilots. 
            \item Created presentations for stakeholders outlining key trends in the data to a non-technical audience. 
            \item \textbf{Liaised} with international clients and took the lead in technical calls to retrieve data requirements.  
        \end{itemize}}
\end{twenty}

\begin{twenty}
    \twentyitem
        {Sept. 2015 - }
        {Present}
        {Oxbridge Applications}
        {\href{http://www.oxbridgeapplications.com}{Premier Tutor \& Mentor}}
        {}
        {\vspace{-1mm} \begin{itemize}
            \item I have to tutor parallel to my studies to finance my degree and living costs; it is \textbf{challenging} to work while studying engineering at Imperial but it has been a rewarding experience. 
            \item I lead problem solving classes in Maths, Physics and Chemistry.
            \item I guide students through the university application process.
           %\item Inspire students' to think beyond the restricted UK mathematics syllabus. 
        \end{itemize}}
\end{twenty}


% \section{Publications}
% L. Antonie, H. Gadgil, G. Grewal, and K. Inwood, “Historical Data Integration - A Study of WWI Canadian Soldiers,” in 2016 IEEE 16th International Conference on Data Mining Workshops (ICDMW), pp. 186-193, IEEE, 2016. \vspace{2mm}

\end{document} 